Practical Machine Learning: Project Writeup
========================================================

## Load data
```{r}
set.seed(123)

training <- read.csv("pml-training.csv",stringsAsFactors=FALSE)
testing <- read.csv("pml-testing.csv",stringsAsFactors=FALSE)
```

## Preprocessing
- divide data into 10 parts, 9 for training, 1 for cross validation
```{r}
library(caret)
folds <- createFolds(y=training$classe,k=10,list=FALSE)
training_trainset <- training[folds!=10,]
training_testset <- training[folds==10,]
```
- due to PC memory issue, use 1% data instead
```{r}
inTrain <- createDataPartition(y=training_trainset$classe,p=0.01,list=FALSE)
inTest <- createDataPartition(y=training_testset$classe,p=0.01,list=FALSE)
```
- take column 8,9,10,11 as predictor, classe as outcome
```{r}
training_trainset_predictor <- training_trainset[inTrain,c(8:11,160)]
training_testset_predictor <- training_testset[inTest,c(8:11,160)]
testing_predictor <- testing[,c(8:11,160)]
```
- transform classe into factor
```{r}
training_trainset_predictor <- transform(training_trainset_predictor,classe=as.factor(classe))
training_testset_predictor <- transform(training_testset_predictor,classe=as.factor(classe))
```

## Training
Apply "Tree Classification"
```{r}
set.seed(123)
modelFit <- train(classe~.,method="rpart",data=training_trainset_predictor)
print(modelFit$finalModel)
```

## Inside Test 
```{r}
y1 <- predict(modelFit,newdata=training_trainset_predictor)
table(training_trainset_predictor$classe)
table(y1)
table(y1==training_trainset_predictor$classe)
```
Train Set Accuracy
```{r}
table(y1==training_trainset_predictor$classe)[2]/sum(table(y1==training_trainset_predictor$classe))
```

## Cross Validation
```{r}
y2 <- predict(modelFit,newdata=training_testset_predictor)
table(training_testset_predictor$classe)
table(y2)
table(y2==training_testset_predictor$classe)
```
Cross Validation Set Accuracy
```{r}
table(y2==training_testset_predictor$classe)[2]/sum(table(y2==training_testset_predictor$classe))
```

## Outside Test
```{r}
y3 <- predict(modelFit,newdata=testing_predictor)
table(y3)
```
Prediction Outcome
```{r}
y3
```

